\texttt{mady}: a Python package for Simulating Generalized Fading Channels

### 2018-03-22 paper/yacoub.tex
changes

\begin{document}
\title{\texttt{yacoub}: a Python package for Simulating Generalized Fading Channels}

\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~J\'unior,}
        \IEEEauthorblockN{~Wamberto~J.~L.~Queiroz,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
\IEEEauthorblockA{Universidade Federal de Campina Grande\\
Instituto Federal de Educa\c c\~ao, Ciencia, e Tecnologia da Para\'iba\\
Campina Grande, Para\'iba, Brasil\\
\{josevinicius,paulo,wamberto,malencar\}@iecom.org.br\\}
}

@@

\begin{abstract}
    We present a well tested Python-based library for simulating and computing
    generalized fading channels, named \texttt{yacoub}. We describe the
    applicability of \texttt{yacoub} using examples in scenarios of communications
    channels impaired by generalized fading, namely: spectrum sensing, bit error
    rate computation, and fading estimation. For the latter, we develop an iterative
    algorithm using the Majorization-Minimization framework, which allows reliable
    estimation of the fading parameter. The development of \texttt{yacoub} is open
    source and its code along with examples are avaliable at
    \texttt{http://github.com/mirca/yacoub}.
\end{abstract}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv, yacoub.bib}

>>>>

\begin{document}
\title{\texttt{mady}: a Python package for Simulating Generalized Fading Channels}

\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Wamberto~J.~L.~Queiroz,}
        \IEEEauthorblockN{~Paulo~R.~Lins~J\'unior,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
\IEEEauthorblockA{Universidade Federal de Campina Grande\\
Instituto Federal de Educa\c c\~ao, Ciencia, e Tecnologia da Para\'iba\\
Campina Grande, Para\'iba, Brasil\\
\{josevinicius,paulo,wamberto,malencar\}@iecom.org.br\\}
}

@@

\begin{abstract}
    We present a well tested Python-based library for simulating and computing
    generalized fading channels, named \texttt{mady}. We describe the
    applicability of \texttt{mady} using examples in scenarios of communications
    channels impaired by generalized fading, namely: spectrum sensing, bit error
    rate computation, and fading estimation. For the latter, we develop an iterative
    algorithm using the Majorization-Minimization framework, which allows reliable
    estimation of the fading parameter. The development of \texttt{mady} is open
    source and its code along with examples are avaliable at
    \texttt{http://github.com/mirca/mady}.
\end{abstract}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv, mady.bib}
